---
title: "Viz"
author: "Qinjing Kang"
date: "2018/1/26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(wesanderson)
library(plyr)
set.seed(1000)
```

### Load data


```{r}
#Load dataset
mh <- read.csv("~/Desktop/survey2.csv", header = TRUE, stringsAsFactors = TRUE)

str(mh)
```

### Cleaning the gender

```{r}
#head(mh$gender)
#levels(mh$gender)
#summary(mh$gender)

#Standardise gender
female = levels(mh$gender)[grep('(fe).*|^f$|fm|woman|female', levels(mh$gender), ignore.case = T, perl = T)]
male  = levels(mh$gender)[grep('^m$|\bmale| male|mail|male |^male| man|\bman|^man$|masculine|dude|^male$', levels(mh$gender), ignore.case = T, perl = T)]
mh$sex = mh$gender
mh$sex[mh$sex %in% female] = 'female'
mh$sex[mh$sex %in% male] = 'male'
mh$sex[!(mh$sex %in% c('male', 'female'))]  = NA 
summary(mh$sex %in% female)
summary(mh$sex %in% male)
summary(!(mh$sex %in% c(male, female)))

mh$sex = droplevels(mh$sex)
table(mh$sex)

#Omit the NA data
mh <- mh %>% filter(sex !="NA")
```


### Frequency

Frequency Distribution and Histogram of all factors

## Frequency Distribution of Number of employee

```{r}
# Omit the self-employeed data
noofemployees <- mh %>% filter(num_employees !="0")
# Make them to be ascending order
noofemployees$num_employees <- factor(noofemployees$num_employees, levels = c("1 to 5","6 to 25","26-100","100-500","500-1000","More than 1000"))
# Plot the distribution
noemployees <- ggplot(noofemployees,aes(num_employees))
noemployees + geom_bar() + geom_text(stat='count',aes(label=..count..),vjust=-1) + ggtitle("Distribution of Number of Employees") + xlab("Number of Employees") + theme_bw()
```

## Frequency Distribution of Tech-company

```{r}
# Omit the self-employeed data
techcomp <- mh %>% filter(tech_company !="n/a")
# Plot the distribution
techcom <- ggplot(techcomp,aes(tech_company))
techcom + geom_bar() + geom_text(stat='count',aes(label=..count..),vjust=-1) + ggtitle("Distribution of Tech Company Or Not") + xlab("0 is No, 1 is Yes") + theme_bw() 
```

## Frequency Distribution of Primary Role

```{r}
# Omit the self-employeed data
primaryrole <- mh %>% filter(primary_role !="n/a")
# Plot the distribution
prirole <- ggplot(primaryrole,aes(primary_role))
prirole + geom_bar() + geom_text(stat='count',aes(label=..count..),vjust=-1) + ggtitle("Distribution of Primary Role is Tech Or Not") + xlab("0 is No, 1 is Yes") + theme_bw()
```

## Frequency Distribution of Currently Have Mental Disorder Or Not

```{r}
# Plot the distribution
CHMD <- ggplot(mh,aes(currently_have_mental_disorder))
CHMD + geom_bar() + geom_text(stat='count',aes(label=..count..),vjust=-1) + ggtitle("Distribution of Currently Have Mental Disorder Or Not") + xlab("") + theme_bw()
```

## Frequency Distribution of Age

```{r}
summary(mh$age)

#Replace the incorrect data with median age
mh[which(mh$age == 3), "age"] <- 33
mh[which(mh$age == 323), "age"] <- 33

# Plot the distribution
ggplot(mh, aes(age)) + geom_histogram() + geom_text(stat='count',aes(label=..count..),vjust=-1) +  ggtitle("Distribution of Ages") + xlab("Age") + theme_bw()

```

## Frequency Distribution of Country Worked

```{r}
# Plot the distribution
CW <- ggplot(mh,aes(country_work))
CW + geom_bar() + geom_text(stat='count',aes(label=..count..),vjust=-1) + ggtitle("Distribution of Country Worked") + xlab("Country Worked") + theme(axis.text = element_text(angle = 90, hjust = 1))
```

## Frequency Distribution of Remote Work Or Not

```{r}
# Plot the distribution
RW <- ggplot(mh,aes(remote_work))
RW + geom_bar() + geom_text(stat='count',aes(label=..count..),vjust=-1) + ggtitle("Distribution of Remote Work Or Not") + theme_bw()
```

### Does Company Size matters?

```{r}
# Group by currently have mental disorder
Company.size <- noofemployees %>% group_by(num_employees,currently_have_mental_disorder)
# Plot
ggplot(Company.size, aes(currently_have_mental_disorder)) + geom_bar() + facet_wrap(~num_employees, scales = "free_y") +
        ggtitle("How many workers Current have mental disorder in different size company?") +
        xlab("Currently with mental disorder?") +
        theme_bw()
# Calculate counts and frequencies
detach("package:plyr", unload=TRUE) 
library(dplyr)
freq1 <- Company.size %>%
  group_by(num_employees,currently_have_mental_disorder) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))
# Plot Frequencies
pfreq1 <- ggplot(freq1, aes(x = num_employees, y = freq, fill = currently_have_mental_disorder)) + geom_bar(stat = "identity") +  xlab("Company Size") + ylab("Frequency") 
ggplotly(pfreq1)
# Is there any relationship between Company Size and Mental Disorder?
# H0:NO
# H1:YES
chisq.test(table(noofemployees$num_employees,noofemployees$currently_have_mental_disorder))
```
Based the result of chi-squared, reject H0, there's no relationship between company size and mental disorder

### Does tech company or not matters?

```{r}
# Group by currently have mental disorder
Tech.company <- techcomp %>% group_by(sex,currently_have_mental_disorder)
# Plot
ggplot(Tech.company, aes(currently_have_mental_disorder)) + geom_bar() + facet_wrap(~tech_company, scales = "free_y") +
        ggtitle("How many employees Current have mental disorder in tech company") +
        xlab("Currently with mental disorder?") +
        theme_bw()
# Calculate counts and frequencies
freq2 <- Tech.company %>%
  group_by(sex,currently_have_mental_disorder) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))
freq2
# Plot Frequencies
pfreq2 <- ggplot(freq2, aes(x = sex, y = freq, fill = currently_have_mental_disorder)) + geom_bar(stat = "identity") +  xlab("Gender") + ylab("Frequency") 
ggplotly(pfreq2)

```
Female workers in tech company suffer more from mental disorder.

### Does tech role or not matters?

```{r}
# Group by currently have mental disorder
Tech.role <- primaryrole %>% group_by(sex,currently_have_mental_disorder)
# Plot
ggplot(Tech.role, aes(currently_have_mental_disorder)) + geom_bar() + facet_wrap(~sex, scales = "free_y") +
        ggtitle("How many tech workers current have mental disorder") +
        xlab("Currently with mental disorder?") +
        theme_bw()
# Calculate counts and frequencies
freq3 <- Tech.role %>%
  group_by(sex,currently_have_mental_disorder) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))
freq3
# Plot Frequencies
pfreq3 <- ggplot(freq3, aes(x = sex, y = freq, fill = currently_have_mental_disorder)) + geom_bar(stat = "identity") +  xlab("Gender") + ylab("Frequency") 
ggplotly(pfreq3)
```
Female tech workers suffer more from mental disorder.

### Does age matters?

```{r}
# Replace 99 with median 33
mh[which(mh$age == 99), "age"] <- 33
# Group by currently have mental disorder
Age.Re <- mh %>% group_by(age,currently_have_mental_disorder)
# Calculate counts and frequencies
library(dplyr)
freq4 <- Age.Re %>%
  group_by(age,currently_have_mental_disorder) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))
freq4
# Plot Frequencies
pfreq4 <- ggplot(freq4, aes(x = age, y = freq, fill = currently_have_mental_disorder)) + geom_bar(stat = "identity") +  xlab("Age") + ylab("Frequency") 
ggplotly(pfreq4)
# Is there any relationship between Company Size and Mental Disorder?
# H0:NO
# H1:YES
chisq.test(table(mh$age,mh$currently_have_mental_disorder))
```
Based the result of chi-squared, reject H0, there's no relationship between age and mental disorder.